Deciding to Disclose

### 2017-04-08 agent_models.tex
Typo 12

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs. Here, the pseudo-count is a hyperparameter of the prior Dirichlet distribution and is nothing more than a hypothetical count of prior observations. The outcome is a result of the relationship between $\alpha$, and $n$, which is increasingly driven by the priors as for higher values of $\alpha$.} for a pair \(i\). Hence,
the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.

>>>>

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{j}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs. Here, the pseudo-count is a hyperparameter of the prior Dirichlet distribution and is nothing more than a hypothetical count of prior observations. The outcome is a result of the relationship between $\alpha$, and $n$, which is increasingly driven by the priors as for higher values of $\alpha$.} for a pair \(j\). Hence,
the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.
